SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-22 paper.tex
review 2. BOUNDED MODEL CHECKING (BMC)

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed by Biere {\it et al.} to verify hardware designs~\cite{Biere99,handbook09}. The authors were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09} was originally proposed by Armando {\it et al.}~\cite{Armando06}.

BMC techniques aims to check the violation of a given (safety) property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ that represents the program correctness and/or the system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in the program, BMC techniques thus unfold the system \textit{k} times, in order to convert it into a verification condition $\psi$, expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

SAT-based or SMT-based BMC procedures have been successfully applied to verify a large number of hardware and software systems, including digital circuits, single- and multi-threaded programs. In general, those BMC techniques were able to find subtle bugs in real digital and embedded software systems, as reported in the literature~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. However, the main criticism with respect to BMC techniques relies on completeness since they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuits implementation or programs with loops whose bounds are too large or cannot be statically determined.

>>>>

Bounded Model Checking (BMC) based on Boolean Satisfiability (SAT) was originally proposed by Biere {\it et al.} to verify hardware designs~\cite{Biere99,handbook09}. The authors were able to successfully verify large digital circuits with approximately $9510$ latches and $9499$ inputs, leading to BMC formulae with $4 \times 10^6$ variables and $1.2 \times 10^7$ clauses to be checked by a standard SAT solver. BMC based on Satisfiability Modulo Theories (SMT)~\cite{BarrettSST09} was originally proposed by Armando {\it et al.}~\cite{Armando06} to deal with increasing software verification complexity.

In general, BMC techniques aims to check the violation of a given (safety) property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of a program; a property $\phi$ that represents the program correctness and/or the system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches, BMC techniques thus unfold the system \textit{k} times, in order to convert it into a verification condition $\psi$, expressed in propositional logic or in a decidable-fragment of first-order logic, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

From the practical point of view, SAT-based or SMT-based BMC procedures have been successfully applied to verify a large number of hardware and software systems, including digital circuits, single- and multi-threaded programs. Those BMC techniques were able to find subtle bugs in real digital and embedded software systems, as reported in the literature~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. However, the main criticism with respect to BMC techniques relies on completeness since they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth.

Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuits implementation or programs with loops whose bounds are too large or cannot be statically determined.
